---
title: "Empirical Project 1 Part 1"
author: "Grace Rotondo"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(DT)
library(janitor)
library(tidyverse)
```

## Question 1
Examine the patterns for a number of different groups (e.g., lowest income children, high income children) and outcomes (e.g., earnings in adulthood, incarceration rates), but only choose one or two of these to include in your project. Describe what you see, and what data are being visualized.

Incarceration rate for all parent income: less than 1%
% staying in same community zone as adults: 46%
Household income for white female of low parent income: $47k
Household income for white female of middle parent income: $55k
Household income for white female of high parent income: $64k
Individual income (excluding spouse) for white children of any parent income: $44k
Individual income (excluding spouse) for white females of any low parent income:$56k
Individual income (excluding spouse) for white females of any middle parent income: $52k
Individual income (excluding spouse) for white females of any high parent income: $48k
College graduation rate of white females of high parent income: 65%
College graduation rate of white females of middle parent income: 52%
College graduation rate of white females of low parent income: 45%


## Question 2
Hypothesis: College graduation rates of white females in Alexandria, Virginia slightly drop depending on the parents' income. E.g. there is a lower college graduation rate of white females coming from a family where the parents had low income, than there is of white females coming from a family where the parents had middle income, and then high income. The household income variable followed the same trend as college graduation. Interestingly, individual income of white females increased as their parental income decreased.

## Question 3
```{r}
atlas <- read_csv("atlas.csv")

Q3 <- atlas %>% 
  select(kfr_pooled_pooled_p25)

Q3
```

